---
title: "Data Dictionary"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Structure 

`datalist.rds` is a list containing `neuro_data`, `obese_data`, and `hit_vec`.  

* `neuro_data` is the processed ToxCast/Tox21 data with 30 chemicals and 131 assay endpoints relevant to neurodevelopmental disorders. 
* `obese_data` is the processed ToxCast/Tox21 data with 30 chemicals and 271 obesity-related assay endpoints. 
* `hit_vec` includes hit-call values based on invitroDBv2 of EPA. 

## Variables 

For `neuro_data` and `obese_data`, 

* `aeid`: assay endpoint ID
* `aenm`: assay endpoint name
* `casn`: CAS registry number 
* `code`: C followed by `casn` without hyphens
* `chnm`: chemical name
* `logc`: log base 10 concentration
* `resp`: response value. 

`hit_vec` has 

* `code`: C followed by `casn` without hyphens
* `aenm`: assay endpoint name
* `hitc`: hit-call value where 1 if active, 0 if inactive, -1 if cannot be determined, and NA if not tested. 

```{r , include = FALSE}
datalist <- readRDS("~/Documents/GitHub/BMC/data/datalist.rds")
```

```{r call data}
names(datalist)
neuro_data <- datalist$neuro_data
obese_data <- datalist$neuro_data
hit_vec <- datalist$hit_vec
```
